---
title: "課題1の補足"
site: bookdown::bookdown_site
output:
  bookdown::gitbook: default
---
##Chapter1
Rには専用のエディタ（コーディングをサポートするソフトウェア）である[Rstudio](https://www.rstudio.com/products/rstudio/download/)という便利な開発環境が用意されているので、各自のPCのOS環境にあったものをインストールしてください。

```{r}
#- ワーキングディレクトリの確認
getwd()
#- ワーキングディレクトリのセット　ドキュメントに設定する場合
# 絶対パス
setwd("C:\\Users\\hiroya\\Documents\\")
# 相対パス
setwd("~\\")

```
##Chapter2
例えば「?関数名とコンソール」に打ち込むと、こんな文章が表示されます。英語の勉強ができますｗ

###Matrices（行列）

###Description（説明）

matrix creates a matrix from the given set of values.

as.matrix attempts to turn its argument into a matrix.

is.matrix tests if its argument is a (strict) matrix.

###Usage（使い方）

matrix(data = NA, nrow = 1, ncol = 1, byrow = FALSE,
       dimnames = NULL)

as.matrix(x, ...)
S3 method for class 'data.frame'
as.matrix(x, rownames.force = NA, ...)

is.matrix(x)

###Arguments（引数）

data	
an optional data vector (including a list or expression vector). Non-atomic classed R objects are coerced by as.vector and all attributes discarded.
nrow	
the desired number of rows.
ncol	
the desired number of columns.
byrow	
logical. If FALSE (the default) the matrix is filled by columns, otherwise the matrix is filled by rows.
dimnames	
A dimnames attribute for the matrix: NULL or a list of length 2 giving the row and column names respectively. An empty list is treated as NULL, and a list of length one as row names. The list can be named, and the list names will be used as names for the dimensions.
x	
an R object.
...	
additional arguments to be passed to or from methods.
rownames.force	
logical indicating if the resulting matrix should have character (rather than NULL) rownames. The default, NA, uses NULL rownames if the data frame has ‘automatic’ row.names or for a zero-row data frame.

```{r}
#- helpメニューが表示される
# help()
#- data.frame関数について調べたいとき　2パターン
# help(matrix)
# ?matrix

#- Helpのサンプルコード
mdat <- matrix(c(1,2,3, 11,12,13), nrow = 2, ncol = 3, byrow = TRUE,
               dimnames = list(c("row1", "row2"),
                               c("C.1", "C.2", "C.3")))
mdat


```
